Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-19 paper/paper.tex
Complete plot and statistical tests subsection

For plotting the data, we first connect again to the Bolt database instance and then filter out only the issues that have 
the variable \emph{Time-To-Close} set (i.e. tickets marked as closed when they were fetched from the Jira instance). Afterwards,
we either save scatter plots or bar charts to disk.

Also, in order to validate our findings, the statistics command fetches all the data from the database and runs two types of 
tests: Welch's T Test \cite{welch1947generalization} for analysing categorical data (e.g. has/does not have attachments)
and Spearman's rank correlation coefficient \cite{spearman1904proof} for investigating continuous data (e.g. how do different 
grammar correctness scores change \emph{Time-To-Close}).

>>>>

For plotting the data, we first connect again to the Bolt database instance and then filter out only the issues that have 
the variable \emph{Time-To-Close} set (i.e. tickets marked as closed when they were fetched from the Jira instance). 
In order to compute correct results, we run the same checks on issues as the ones listed in the analyse command (e.g. plot 
only tickets of high priority). Afterwards, we either save scatter plots or bar charts to disk presenting correlations 
between all the variables we tested.

In terms of technology used for plotting the data, we have used a library called go-chart \cite{go-chart} created by 
Will Charczuk. It is an extensible library with a focus on extensability - it does not provide the end user a large number 
of default options, but rather let him/her extend their graphs as much as it is needed (e.g. add specific labels for axes, 
plot a secondary Y axis).

Also, in order to validate our findings, the statistics command fetches all the data from the database and runs two types of 
tests: Welch's T Test \cite{welch1947generalization} for analysing categorical data (e.g. has/does not have attachments)
and Spearman's rank correlation coefficient \cite{spearman1904proof} for investigating continuous data (e.g. how do different 
grammar correctness scores change \emph{Time-To-Close}). For computing Spearman R Tests we made use of a simple 
statistics library created by Damian Gryski called onlinestats \cite{onlinestats}, while for Welch T Tests we created our 
own custom types and functions.

They have both been created with extensability in mind - we believe that in the future work we proposed to conduct on the 
project, we might need to use other statistical tests as well, such as Mann-Whitney U tests \cite{mann1947test}. Also, before
we ran both statistical tests and the plotting command, we tested them thoroughly and checked whether the libraries compute 
stable and robust results.
